---
title: "25 examples"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


# Welcome 
This is a small list with 25 visualization using gt Package.  

## What is this?  

GT package is one of the most amazing package to create tables, and we want to show a gallery of examples with full R code to encourage you to use it in your projects.

* How to start with GT Tables
* How to customize a basic table
* Examples about how to use


## How to create a good table?
An informal definition could be: "A good table is used to read a set of numerical data in the quickest and easiest way"


# 25 examples about how to use this amazing package

## 1. Vertical table
```{r vertical_table, message=FALSE, warning=TRUE, paged.print=FALSE}
library(gt)
library(tidyverse)
library(glue)

# Define the start and end dates for the data range
start_date <- "2010-06-07"
end_date <- "2010-06-14"

# Create a gt table based on preprocessed
# `sp500` table data
sp500 %>%
  dplyr::filter(date >= start_date & date <= end_date) %>%
  dplyr::select(-adj_close) %>%
  dplyr::mutate(date = as.character(date)) %>%
  gt() %>%
  tab_header(
    title = "S&P 500",
    subtitle = glue::glue("{start_date} to {end_date}")
  ) %>%
  fmt_date(
    columns = vars(date),
    date_style = 3
  ) %>%
  fmt_currency(
    columns = vars(open, high, low, close),
    currency = "USD"
  ) %>%
  fmt_number(
    columns = vars(volume),
    scale_by = 1 / 1E9,
    pattern = "{x}B"
  )
```

## 2. Horizontal table

## 3. Table with references 
This example is from [Table
1](http://www.aclweb.org/anthology/W11-0705)
From proceedings of the Workshop on Language in Social Media (LSM 2011), pages 30–38, Portland, Oregon, 23 June 2011. (c) 2011 Association for Computational Linguistics

```{r tab3_reference}
# the table's data
exa <- data.frame( acronym = c("gr8, gr8t", "lol", "rotf", "bff"),
                  english = c("great","laughing out loud", "rolling on the floor", "best friend forever"))

# create the gt table
gt(exa) %>%
  cols_align("left") %>%
  cols_label(acronym="Acronym",
             english="English expansion") %>%
  tab_source_note(
    source_note = "Table 1: Example acrynom and their expansion in the acronym dictionary."
  ) 

```

## 4. Table with spanning columns

This example is [Table
S2](http://www.genetics.org/content/genetics/suppl/2012/06/28/genetics.112.142448.DC1/TableS2.pdf)
in [Broman et al. (2015) Genetics 192:267-279
doi:10.1534/genetics.112.142448](https://doi.org/10.1534/genetics.112.142448)

```{r tab4_spanners}
# the table's data
tab <- data.frame(n=c(300, 450, 600),
                  all_part_all_crosses = c(4.56, 4.51, 4.49),
                  all_part_min_crosses = c(4.48, 4.47, 4.44),
                  tree_part_all_crosses = c(4.43, 4.36, 4.32),
                  tree_part_min_crosses = c(4.33, 4.33, 4.29))

# create the gt table
gt(tab) %>%
    cols_align("center") %>%
    cols_label(n="total sample size",
               all_part_all_crosses="all crosses",
               all_part_min_crosses="min crosses",
               tree_part_all_crosses="all crosses",
               tree_part_min_crosses="min crosses") %>%
    tab_spanner(label="Tree partitions",
                starts_with("tree")) %>%
    tab_spanner(label="All partitions",
                starts_with("all"))
```

