---
title: "25 examples"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


# Welcome
This is a small list with 25 visualization using gt Package.

## What is this?

GT package is one of the most amazing package to create tables, and we want to show a gallery of examples with full R code to encourage you to use it in your projects.

* How to start with GT Tables
* How to customize a basic table
* Examples about how to use


## How to create a good table?
An informal definition could be: "A good table is used to read a set of numerical data in the quickest and easiest way"


# 25 examples about how to use this amazing package

## 1. Vertical table
```{r vertical_table, message=FALSE, warning=TRUE, paged.print=FALSE}
library(gt)
library(tidyverse)
library(glue)

# Define the start and end dates for the data range
start_date <- "2010-06-07"
end_date <- "2010-06-14"

# Create a gt table based on preprocessed
# `sp500` table data
sp500 %>%
  dplyr::filter(date >= start_date & date <= end_date) %>%
  dplyr::select(-adj_close) %>%
  dplyr::mutate(date = as.character(date)) %>%
  gt() %>%
  tab_header(
    title = "S&P 500",
    subtitle = glue::glue("{start_date} to {end_date}")
  ) %>%
  fmt_date(
    columns = vars(date),
    date_style = 3
  ) %>%
  fmt_currency(
    columns = vars(open, high, low, close),
    currency = "USD"
  ) %>%
  fmt_number(
    columns = vars(volume),
    scale_by = 1 / 1E9,
    pattern = "{x}B"
  )
```

## 2. Horizontal Table 

## 3. Table with references

This example is from [Table
1](http://www.aclweb.org/anthology/W11-0705)
From proceedings of the Workshop on Language in Social Media (LSM 2011), pages 30–38, Portland, Oregon, 23 June 2011. (c) 2011 Association for Computational Linguistics

```{r tab2_reference}
# the table's data
exa <- data.frame( acronym = c("gr8, gr8t", "lol", "rotf", "bff"),
                  english = c("great","laughing out loud", "rolling on the floor", "best friend forever"))

# create the gt table
gt(exa) %>%
  cols_align("left") %>%
  cols_label(acronym="Acronym",
             english="English expansion") %>%
  tab_source_note(
    source_note = "Table 1: Example acronym and their expansion in the acronym dictionary."
  )

```

## 3. Table with spanning columns

This example is [Table
S2](http://www.genetics.org/content/genetics/suppl/2012/06/28/genetics.112.142448.DC1/TableS2.pdf)
in [Broman et al. (2015) Genetics 192:267-279
doi:10.1534/genetics.112.142448](https://doi.org/10.1534/genetics.112.142448)

```{r tab3_spanners}
# the table's data
tab <- data.frame(n=c(300, 450, 600),
                  all_part_all_crosses = c(4.56, 4.51, 4.49),
                  all_part_min_crosses = c(4.48, 4.47, 4.44),
                  tree_part_all_crosses = c(4.43, 4.36, 4.32),
                  tree_part_min_crosses = c(4.33, 4.33, 4.29))

# create the gt table
gt(tab) %>%
    cols_align("center") %>%
    cols_label(n="total sample size",
               all_part_all_crosses="all crosses",
               all_part_min_crosses="min crosses",
               tree_part_all_crosses="all crosses",
               tree_part_min_crosses="min crosses") %>%
    tab_spanner(label="Tree partitions",
                starts_with("tree")) %>%
    tab_spanner(label="All partitions",
                starts_with("all"))
```


## 4. Counts and percentages

This example is Table S2 of [Lobo et al. bioRxiv
doi:10.1101/529040](https://doi.org/10.1101/529040), with columns
containing both counts and percentages, with the percentages in
parentheses.

```{r tab4_counts_and_percents}
tab <- data.frame(A_count = c(8863572, 2870063, 671722),
                  A_proportion=c(0.85360, 0.72748, 0.55618),
                  B_count = c(1520169, 1075126, 536010),
                  B_proportion=c(0.14640, 0.27252, 0.44382),
                  row.names=c("AA", "AB", "BB"))
tab$genotype <- rownames(tab)

gt(tab, rowname_col="genotype") %>%
    fmt_percent(ends_with("proportion"),
                decimals=1,
                pattern="({x})") %>%
    cols_align("center") %>%
    cols_align("right", columns=ends_with("count")) %>%
    cols_label(A_count = "A count",
               A_proportion = "(%)",
               B_count = "B count",
               B_proportion = "(%)") %>%
    tab_spanner(label="allele in DO-360 microbiome",
                columns=TRUE) %>%
    tab_stubhead_label("DO-360 genotype")
```

## 5. Counts and percentages, with an extra column.

This example is Table S4 of [Lobo et al. bioRxiv
doi:10.1101/529040](https://doi.org/10.1101/529040).
It is much like example 5, but has an additional column at the beginning.

```{r tab5_counts_and_percents}
tab <- data.frame(DO358_genotype = c("AA", "AA", "AA", "AB", "AB", "AB", "BB", "BB", "BB"),
                  DO344_genotype = c("AA", "AB", "BB", "AA", "AB", "BB", "AA", "AB", "BB"),
                  A_count = c(2394215, 869613, 103036, 686970, 297500, 55982, 73727, 47000, 542),
                  A_proportion = c(0.99748, 0.79482, 0.59091,
                                   0.71827, 0.51430, 0.29922,
                                   0.42869, 0.21910, 0.00458),
                   B_count = c(6050, 224483, 71332, 269447, 280958, 131111, 98257, 167513, 117802),
                   B_proportion = c(0.00252, 0.20518, 0.40909,
                                    0.28173, 0.48570, 0.70078,
                                    0.57131, 0.78090, 0.99542),
                   stringsAsFactors=FALSE)

gt(tab) %>%
    fmt_percent(ends_with("proportion"),
                decimals=1,
                pattern="({x})") %>%
    cols_align("right") %>%
    cols_align("center", columns=ends_with("genotype")) %>%
    cols_label(DO358_genotype="DO 358 genotype",
               DO344_genotype="DO 344 genotype",
               A_count = "A count",
               A_proportion = "(%)",
               B_count = "B count",
               B_proportion = "(%)") %>%
    tab_spanner(label="allele in DO-358 microbiome",
                columns=matches("^[AB]_"))
```



## 6. Adding colors from Viridis palette

This example is using the dataset gtcars included into gt package and Viridis palette. 
```{r tab6_colors_from_viridis_palette}
library(tidyverse) 
library(viridis)
library(scales)
library(gt) 

#selecting the data
exa2 <- gtcars %>% 
  select(mfr, hp) %>% 
  group_by(mfr) %>% 
  summarise(mean(hp))

#choosing colors
q_colors =  19 
v_colors =  viridis(q_colors, option ="D")

#creating table
gt(exa2) %>% 
  data_color(columns=vars("mean(hp)"), 
             color=scales::col_bin( bins=c(100, 200, 300, 400, 500, 600,700), 
             palette = v_colors, 
             domain=c(0, 700)) ) 
```

## 7. Table of coefficients

For a table of estimated regression coefficients from the fit of a
linear model, you might first want to use the
[broom](https://broom.tidyverse.org) package to tidy the output.

```{r tab7_lm_broom}
lm_out <- lm(Volume ~ Height * Girth, data=trees)
broom::tidy(lm_out) %>%
    gt(rowname_col="term") %>%
    tab_stubhead_label("term") %>%
    fmt_number(column=matches("^[^p]"), decimals=2) %>%
    fmt_number(column=matches("^p"), decimals=6) %>%
    cols_align("left", column=matches("^p")) %>%
    cols_label(std.error="SE",
               statistic="t stat",
	       p.value="P value")
```


## 8. Compare fit of multiple models

To compare the fit of multiple models, you may be interested in the
[gt summary](https://github.com/vincentarelbundock/gtsummary) package.
For example, here is a comparison of the fit of a linear model with and
without an interaction term.

```{r tab8_gt}
lm_add <- lm(Volume ~ Height + Girth, data=trees)
lm_int <- lm(Volume ~ Height * Girth, data=trees)
list(add=lm_add, int=lm_int) %>%
    gtsummary::gtsummary(statistic="conf.int") %>%
    cols_label(add="Additive",
               int="Interactive")

```
